### 2020-06-25 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

    Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
    (see Appendix \ref{app::ResearchSummary}). We now analyse the stability of this dynamical system
    by linearising about
    a
    fixed point. This yields the requirement that a fixed point $x^*$ satisfy

@@

    The implication here is that the resulting value of $x^*$ can take two solutions. However, one of these is $x^* = 0$, which is found to rarely occur, while the second solution contains a term $\sqrt{\Gamma}$, which would yield complex values. If this is true, then it would imply that the learning algorithm will rarely converge for values of $\Gamma < 0$. Numerical experiments will shed more light on the likelihood of convergence. If this ansatz turns out to be incorrect (i.e. we see significant convergence for $\Gamma < 0$), it is unlikely that we will be able to solve for the stability line for this case.

    We take the Fourier transform of this system to determine the long term behaviour of thhe system
    after a disturbance. To neglect all transient behaviour, we consider the equation at $\omega =
    0$

@@

    By
    considering that $\left<[|\mathcal{X}(\omega =
    0)|^2
    \right> \geq 0$  we arrive at an expression for a stability line (i.e. the phase transition
    between the
    existence of stable fixed points and unstable behaviour) as the equality (\ref{eqn::Transformed}
    )$>0$.

@@

\begin{enumerate}
    \item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
    it does not affect the long term behaviour of the system (it does not appear in (
    \ref{eqn::EOM})).
    \item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
    over.
    \item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
    (variables are the payoff elements) with covariance parameterised by $\Gamma$.
    \item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
    \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
    \item Every 100 iterations, check to see if the action probabilities have changed significantly.
    If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
    considered to have converged.
    \item This process is repeated 5 times with random payoff matrices generated based on the value
    of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
    converged}}{5}$.
    \item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
    heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
    tested.
\end{enumerate}

@@

    As mentioned, the above system considers only a two player game. This was done with the intention
    of simplifying the notation and reducing the complexity of the experiments. However, the next
    immediate action is to present the equivalent solutions for the case of a general p-player game.

>>>>

    Here, $G, \rho, \eta, \mu$ are correlation functions, generated due to the averaging process 
    and the notation $\tilde{\cdot}$ denotes a term which has been scaled with respect to $N$ (see
    Appendix \ref{app::ResearchSummary} for method and notation). We now analyse the stability of
    this dynamical system by linearising about a fixed point. This yields the requirement that a
    fixed point $x^*$ satisfy

@@

    The implication here is that the resulting value of $x^*$ can take two solutions. However, one
    of these is $x^* = 0$, which is found to rarely occur \cite{Coolen2005}, while the second solution
    contains a term $\sqrt{\Gamma}$, which would yield complex values. Such a result, of course, is
    not possible for a quantity denoting probabilities and so it appears that the theory cannot hold
    for $\Gamma < 0$. However, numerical experiments will shed light on the likelihood of
    convergence and the islands of stability in parameter space for this region.

    We take the Fourier transform of this system to determine the long term behaviour of the system
    after a disturbance. To neglect all transient behaviour (high frequency disturbances), we
    consider the equation at $\omega = 0$

@@

    By
    considering that $\left<|\mathcal{X}(\omega =
    0)|^2
    \right> \geq 0$  we arrive at an expression for a stability line (i.e. the phase transition
    between the
    existence of stable fixed points and unstable behaviour) as the equality (\ref{eqn::Transformed}
    )$>0$.

@@

\begin{enumerate}
    \item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
    it does not affect the long term behaviour of the system (it does not appear in (
    \ref{eqn::EOM})).
    \item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
    over.
    \item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
    (variables are the payoff elements) with covariance parameterised by $\Gamma$.
    \item Initialise the agents with random initial conditions (i.e. random action probabilities).
    \item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
    \item Every 100 iterations, check to see if the action probabilities have changed significantly.
    If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
    considered to have converged.
    \item This process is repeated 5 times with random payoff matrices generated based on the value
    of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
    converged}}{5}$.
    \item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
    heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
    tested.
\end{enumerate}

@@

    As mentioned, the above system considers only a two player game. This was done with the intention
    of simplifying the notation and reducing the complexity of the experiments. However, the next
    immediate action is to present the equivalent solutions for the case of a general $p$-player
    game.
